% SPDX-License-Identifier: 0BSD
\documentclass[10pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper,margin=0.75in,headheight=21pt]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{siunitx}
\usepackage[table]{xcolor}

\definecolor{ReportInk}{HTML}{17212B}
\definecolor{ReportBlue}{HTML}{145A86}
\definecolor{ReportGreen}{HTML}{287A58}
\definecolor{ReportOrange}{HTML}{B76E00}
\definecolor{ReportRed}{HTML}{B33A3A}
\definecolor{ReportRule}{HTML}{CBD3DA}
\definecolor{ReportMuted}{HTML}{66717C}
\definecolor{refblue}{HTML}{DCEBFF}
\definecolor{bestgreen}{HTML}{DFF5E4}
\definecolor{speedgreen}{HTML}{1A7F37}
\definecolor{speedorange}{HTML}{BF8700}
\definecolor{speedred}{HTML}{CF222E}

\hypersetup{
  colorlinks=true,
  linkcolor=ReportBlue,
  urlcolor=ReportBlue,
  pdftitle={pyAmpliCol 0.1.0 Methodology and Performance Report},
  pdfauthor={Rikkert Frederix, Valentin Hirschi, and Timea Vitos}
}
\sisetup{detect-all,scientific-notation=true,round-mode=figures,round-precision=3}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{1}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{ReportInk}{pyAmpliCol 0.1.0}}
\fancyhead[R]{\textcolor{ReportMuted}{Methodology and performance}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{ReportRule}\leaders\hrule height \headrulewidth\hfill}}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcommand{\PAC}{\texttt{pyAmpliCol}}
\newcommand{\AC}{\texttt{AmpliCol}}
\newcommand{\ReportNA}{\textcolor{ReportMuted}{\textsc{n/a}}}
\newcommand{\ReportStatus}[1]{\textcolor{ReportMuted}{\textsc{#1}}}
\newcommand{\ReportMetricCell}[2]{\shortstack{\textcolor{ReportGreen}{G #1}\\\textcolor{ReportBlue}{R #2}}}
\newcommand{\ReportTableNote}[1]{\par\smallskip\noindent\footnotesize\textcolor{ReportMuted}{#1}\par}
\newcommand{\ReportMatrixLegend}{\ReportTableNote{Cell ordering and units follow the reading guide at the start of this section. A slash separates the two AmpliCol LC runtime workloads; a vertical bar separates the pyAmpliCol Rusticol-core wall and evaluator-only multipliers. Every multiplier is pyAmpliCol divided by AmpliCol.}}
\newcommand{\ReportLadderLegend}{\ReportTableNote{Each workload block reports generation in seconds and Rusticol-core wall and evaluator-only runtime in microseconds per point. Parenthesized multipliers compare pyAmpliCol with AmpliCol; the UFO-SM ``vs blt-in'' columns compare the same UFO-SM and built-in-SM setup.}}
\newcommand{\ReportLandscapeFooter}{}

\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  frame=single,
  rulecolor=\color{ReportRule},
  breaklines=true,
  showstringspaces=false,
  xleftmargin=0.5em,
  xrightmargin=0.5em
}

\title{\vspace{-1.4cm}\textbf{pyAmpliCol 0.1.0}\\[0.35em]
  \Large Methodology and Performance Report}
\author{Rikkert Frederix \and Valentin Hirschi \and Timea Vitos}
\date{Release 0.1.0}

\begin{document}
\maketitle

\begin{abstract}
This report defines the public theory, validation, and performance methodology
for \PAC{}, release 0.1.0. It fixes the canonical process coverage for the
built-in Standard Model, the same physics loaded as a UFO/JSON Standard Model
(UFO-SM), a scalar contact model, and a scalar-gravity model. Its tables present
reproducible measurements tied to an effective configuration, execution
environment, generated artifact, and independent-reference provenance.
\end{abstract}

\begingroup
\small
\setlength{\parskip}{0pt}
\tableofcontents
\endgroup
\clearpage

\section{Scope}

\PAC{} generates tree-level scattering-amplitude artifacts and evaluates them
through the Rusticol runtime. The Python layer resolves models and processes,
constructs a shared-current directed acyclic graph (DAG), lowers bounded stages
to Symbolica evaluators, and writes a versioned process artifact. The runtime
loads that artifact and provides summed and resolved evaluation through one
physics contract to Python, Rust 2021, C++17, and Fortran 2008 clients.

The report has three purposes:
\begin{enumerate}
  \item specify the observables and conditions required for a publishable
        benchmark;
  \item preserve a stable matrix of representative process families and colour
        approximations; and
  \item separate measured data from prose by rendering every result table from
        validated measurement records.
\end{enumerate}

An \ReportNA{} entry means that the current result set has no recorded measurement
for that slot. It is neither a zero, a failure, nor a value carried over from
another implementation. Explicit failure labels such as \ReportStatus{t/o},
\ReportStatus{RAM>limit}, \ReportStatus{VALIDATION FAILED}, and
\ReportStatus{ERROR} identify a recorded timeout, resource limit, numerical
mismatch, or execution failure rather than a physics value.

\section{Current Recursion and Model Lowering}

\subsection{Shared-current DAG}

For an external subset $I$, particle state $t$, and local spin or flow label
$\chi$, an off-shell current has the schematic recursion
\begin{equation}
  J^{\alpha}_{t,\chi}(I)
  = P^{\alpha}{}_{\beta}(t,p_I)
    \sum_{I=A\mathbin{\dot\cup}B}
    V^{\beta}{}_{\gamma\delta}(t_A,t_B\!\to t)
    J^{\gamma}_{t_A,\chi_A}(A)
    J^{\delta}_{t_B,\chi_B}(B),
  \qquad p_I=\sum_{i\in I}p_i .
  \label{eq:recursion}
\end{equation}
Current identity includes the particle, external labels, helicity ancestry,
chirality or spin state, flavour and charge flow, colour state, momentum mask,
and any auxiliary-current kind. Contributions with the same complete identity
share one node. A topological sweep therefore evaluates each retained current
once per phase-space point and reuses it in all dependent amplitudes.

External UFO or serialized JSON sources are compiled to the same canonical
model representation as the process generator consumes. Particle metadata,
interactions, coupling orders, Lorentz tensors, colour tensors, propagators,
and runtime parameters come from that representation. UFO directories contain
trusted executable Python; serialized JSON is the portable data-only source.

Optimizations on the external-model path are proof-gated rather than selected
by particle names or PDG values. Exact normalized colour and Lorentz
expressions, propagator metadata, and coupling relations certify current
reflection, helicity, and reusable-kernel identities. For overlapping
Standard-Model validation processes, the resulting current, interaction,
amplitude-root, and colour-sector counts must match the built-in compatibility
model after applying the same independently inferred perturbative-order
envelope. An external compiler may retain fewer evaluator calls only when an
additional exact kernel-equivalence certificate proves that reuse.

\subsection{Contact terms and spin two}

A vertex with valence above three is lowered to a deterministic tree of
non-propagating auxiliary currents. The construction inserts the original
coupling once and introduces no pole. Direct contraction of the original
contact tensor is the validation oracle for the scalar-contact ladder.

The scalar-gravity ladder exercises rank-two external states and
momentum-dependent interactions. For a massless graviton, the helicity-two
polarization tensor is represented as
\begin{equation}
  \epsilon^{\mu\nu}_{\pm 2}
  = \epsilon^{\mu}_{\pm}\epsilon^{\nu}_{\pm} .
\end{equation}
Validation checks symmetry, transversality, tracelessness, normalization, and
agreement between ordinary and higher-precision evaluation.

\section{Colour and Runtime Semantics}

The process matrices use three colour contracts:
\begin{center}
\begin{tabular}{@{}L{0.45in}L{5.85in}@{}}
\textbf{LC} & Leading-colour ordered amplitudes with physical colour-flow selectors. \\
\textbf{NLC} & The leading term plus the first retained $1/N_c^2$-suppressed contribution. \\
\textbf{Full} & The complete supported sparse colour metric for the generated amplitude basis. \\
\end{tabular}
\end{center}

For NLC, ``retained'' applies to a colour-matrix \emph{entry}, not to a
truncated numerical coefficient.  Write the exact overlap of two colour-flow
tensors as
\begin{equation}
  C_{ab}(N_c)=\sum_p c^{(ab)}_p N_c^p,
  \qquad
  p_{ab}=\max\{p:c^{(ab)}_p\ne0\},
  \label{eq:nlc-entry-gate}
\end{equation}
and let \(P\) be the leading power of the complete colour basis.  The sparse
NLC metric used by
\texttt{build\_color\_}\allowbreak\texttt{contraction\_plan()} in
\path{src/pyamplicol/color/contraction.py} is
\begin{equation}
  C^{\mathrm{NLC}}_{ab}=
  \begin{cases}
    C_{ab}(3), & p_{ab}\ge P-2,\\
    0,         & p_{ab}<P-2.
  \end{cases}
  \label{eq:nlc-exact-coefficient}
\end{equation}
Thus every qualifying entry keeps all of its finite-\(N_c\) terms.  For three
open fundamental lines and one adjoint, \(P=4\).  Representative retained
off-diagonal overlaps are

\begin{center}
\begin{tabular}{@{}L{1.45in}L{1.20in}L{1.35in}L{1.35in}@{}}
\toprule
\textbf{exact overlap} & \textbf{highest power} &
  \textbf{NLC at \(N_c=3\)} & \textbf{full at \(N_c=3\)} \\
\midrule
\(-N_c^3+N_c\) & \(3\) & \(-24\) & \(-24\) \\
\(N_c^2-1\) & \(2\) & \(8\) & \(8\) \\
\bottomrule
\end{tabular}
\end{center}

The implementation in
\path{src/pyamplicol/color/contraction_factors.py} carries these powers as
exact rational coefficients.  The upper-triangular runtime plan applies a
separate factor of two to off-diagonal interference terms; that storage
factor must not be confused with the colour coefficient in
Eq.~\eqref{eq:nlc-exact-coefficient}.

The optimized \texttt{Runtime.evaluate()} path returns one summed matrix
element per point.\par
The resolved method \texttt{Runtime.}\allowbreak\texttt{evaluate\_resolved()} exposes LC values with
axes \texttt{(point, helicity, flow)}. NLC and full-colour artifacts expose one
already contracted colour component per helicity. Summing all non-point axes
must reproduce the optimized total. Public selectors use physical helicity and
flow identifiers; graph-local colour-sector identifiers are not report inputs.

All language bindings load the same process manifest and evaluator payloads.
Cross-language agreement therefore validates the runtime interfaces and data
layout. A separately generated reference is required for an independent
physics comparison.

The default JIT artifact embeds a self-contained SymJIT application for f64
evaluation. Rusticol executes that payload through the separate MIT-licensed
SymJIT runtime without importing Symbolica or consulting its runtime license
state. Compiled ASM and C++ f64 payloads are likewise loaded directly by the
native core. Python evaluation above f64 precision uses the retained Symbolica
evaluator state and therefore requires Symbolica at runtime.

\section{Benchmark Methodology}

\subsection{Configuration contract}

Each measurement begins from an immutable resolved configuration. Unless a
table variant says otherwise, the report contract uses the release defaults:
requested SymJIT optimization level 3, evaluator batch size 128, output chunk size
128, stage-local parameter layout, ten Horner iterations, backend-default
common-pair elimination, a ten-second benchmark target, two warmup runs, and at
least five timed samples. The process matrices always request level 3; only
explicitly labelled comparison rows, such as JIT level 1 in the dedicated $Z$
ladder, override it. SymJIT may apply its documented backend fallback
independently of the requested level. Requested and effective configurations
are retained separately so resource or license adjustments remain visible.

Generation time is wall time for one explicit \texttt{Generator.generate()}
operation starting from an already compiled canonical model and ending with a
committed, loadable process artifact. It includes process expansion, DAG and
evaluator construction, evaluator compilation, validation-point preparation,
and API-bundle emission. Loading and compiling the UFO/JSON or built-in model
is performed before the generation timer, passed to either ordinary generation
or the selected \texttt{GenerationSlice}, and recorded separately as
\texttt{model\_precompile\_seconds}. It is not included in a process-generation
cell. Existing artifacts may be benchmarked, but their generation slot remains
\ReportNA{} unless a matching generation measurement is available.

Runtime measurements use \texttt{BenchmarkRunner} and the summed
\texttt{Runtime.evaluate()} observable. The reported wall time begins inside
Rusticol after caller-language array conversion and covers repeated ordinary
core evaluations, including source preparation, stage input packing, evaluator
calls, output assignment, and reduction. The evaluator time is the subset spent
inside the generated stage and amplitude evaluators. Python/NumPy packing and
language-binding conversion are therefore excluded from both. A measurement
records sample count, time per point, uncertainty, effective settings, and
environment. Comparisons are valid only for the same process, colour accuracy,
parameters, phase-space ensemble, precision, selectors, and normalization.

\subsection{Benchmark platform}

The populated measurements in this report were produced on the cluster host
\texttt{itphlies.clan} from the Nix developer shell, not from a scheduler-visible
batch partition in the reporting environment.  The node reports Linux
\texttt{6.12.63} on NixOS \texttt{26.05}, \texttt{x86\_64}, glibc \texttt{2.42}.
The processor is a dual-socket AMD EPYC 9754 system (Genoa/Zen~4): 256 physical
cores are visible across eight NUMA nodes, with 384 logical CPUs online in this
session.  The advertised instruction-set families include SSE through SSE4.2,
FMA, AVX, AVX2, AVX-512 foundation/vector, VNNI/BF16, AES/SHA, BMI1/2, ADX,
VAES, and carry-less multiplication.  Installed memory reported by the kernel
is \texttt{1188419660 kB} (\(\simeq 1.11\) TiB), with no configured swap.

All report measurements use the repository's developer installation through
\texttt{.venv/bin/python} inside \texttt{nix develop}.  The effective toolchain
for the current campaign is Python \texttt{3.11.15} with NumPy \texttt{2.4.2},
Rust \texttt{1.89.0}, Cargo \texttt{1.89.0}, GCC/G++/GNU Fortran
\texttt{15.2.0}, and pdfTeX \texttt{3.141592653-2.6-1.40.27} from TeX Live
2025.  The campaign commands enforce an 800~GiB RSS limit, a 3600~s generation
timeout per cell generation workload, and a 20~s target runtime for benchmark
sampling.  Unless a cell's manifest states otherwise, each cell uses one
generation/evaluator core (\texttt{--cell-cores 1}); the current table-filling
batches use up to eight concurrent process workers with
\texttt{--allow-symbolica-parallel}, while the earlier scalar-ladder
cross-check used one process worker with the same per-cell core and timing
policy.  Wall times are native Rusticol repeated-core timings after
caller-language momentum packing, and model compilation is recorded separately
from process-generation time.

\subsection{Numerical validation}

The matrix element and its independent reference are evaluated at the same
deterministic points with the same parameter card. Shared-core language checks
use relative tolerance $10^{-12}$ and absolute tolerance $10^{-15}$.
Independent reference comparisons use relative tolerance $10^{-8}$, with
higher precision used to diagnose unstable points. A populated result must
also satisfy the resolved-sum identity and preserve expected structural zeros.

No timing is accepted as a numerical validation result. Conversely, a valid
matrix element does not populate generation or runtime fields without a
matching timing run.

\paragraph{Result provenance.}

Each displayed number is retained with its resolved configuration, software
revision, hardware and execution environment, numerical check, and timing
statistics. A result enters the report only after its record is internally
consistent and its pointwise comparison has the status required by the table.

\clearpage
\begin{landscape}
\pagestyle{empty}
\section{Standard-Model Process Matrices}

The canonical matrix spans electroweak vector production, charged-current and
leptonic channels, heavy-quark production, pure gluons, multi-boson final
states, Higgs-associated final states, and three- and four-quark-line cases.
Here $n$ is the number of final-state particles. LC coverage retains the
declared grid through $n=9$, with the four bounded families ending at
$n=8$. NLC and full-colour grids retain $n=1,\ldots,5$; cells below a family's
minimum physical multiplicity remain explicitly marked \ReportNA{}.

The UFO-SM matrices use the same process definitions, colour contracts, and
numerical input parameters as the built-in-SM matrices. Their source is the
packaged Standard Model loaded through the generic UFO/JSON compiler. The
comparison therefore isolates model loading and generic lowering without
changing the requested physics or the original Fortran \AC{} reference.

\subsection*{How to read a process-matrix cell}

Every process-matrix comparison uses \PAC{} JIT at requested optimization level
3. The process matrices do not include ASM or C++ measurements; those backends
appear in the dedicated $Z$ ladder. For a time $T$, a parenthesized
$\texttt{x}r$ is the dimensionless ratio
\begin{equation}
  r = \frac{T_{\text{\PAC{}}}}{T_{\text{\AC{}}}}.
  \label{eq:matrix-time-ratio}
\end{equation}
Green, orange, and red denote respectively $r<1$, $1\leq r<2$, and $r\geq2$;
thus green means that \PAC{} is faster. The compact layout is:

\begin{center}
\small
\begin{tabular}{@{}L{0.82in}L{2.30in}L{5.95in}@{}}
\toprule
\textbf{contract} & \textbf{line and reference entry} & \textbf{pyAmpliCol entries} \\
\midrule
LC, upper & \AC{} generation time in seconds & selected-flow/helicity-sum generation ratio; all-flows/fixed-helicity generation ratio \\
LC, lower & \AC{} selected-flow/all-flows runtimes in microseconds per point, separated by ``/'' & for each workload, \texttt{(xwall$\mid$eval)} gives the Rusticol-core wall and evaluator-only ratios against the matching \AC{} runtime \\
NLC/full, upper & \AC{} generation time in seconds & \PAC{} JIT O3 generation ratio \\
NLC/full, lower & \AC{} fully contracted runtime in microseconds per point & \texttt{(xwall$\mid$eval)} gives the Rusticol-core wall and evaluator-only ratios against that runtime \\
\bottomrule
\end{tabular}
\end{center}

The two LC generation ratios correspond to separately generated selected-flow
and complete-flow \PAC{} artifacts. \AC{} generates one library that supports
both runtime workloads, so the same \AC{} generation time is the denominator
of both ratios. ``Selected flow, helicity sum'' evaluates one matched physical
LC ordering and sums all supported helicities. ``All flows, fixed helicity''
evaluates every represented physical LC ordering for one supported helicity.
NLC and full colour instead report one helicity-summed, fully
colour-contracted workload; no per-flow scalar is defined for those contracts.

At the foot of each multiplicity column, every summary cell has two lines. The
first contains the \AC{} values as
\texttt{min$\mid$max$\mid$mean$\mid$median}; generation is in seconds
and runtime in microseconds per point. The second contains the paired \PAC{}/
\AC{} multipliers as
\texttt{min$\mid$max$\mid$mean$\mid$median$\mid$ratio-of-sums}, where the
last field is
$\sum_i T_{\text{\PAC{}},i}/\sum_i T_{\text{\AC{}},i}$ over the same valid
process pairs. LC provides separate generation and runtime summary rows for its
two workloads. NLC and full colour provide generation, core-wall runtime, and
evaluator-only runtime rows; the last two share the same \AC{} reference runtime
because \AC{} has no corresponding evaluator-only timing split.

\clearpage
\input{result_matrix_builtin_sm_lc_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\clearpage
\input{result_matrix_builtin_sm_nlc_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\clearpage
\input{result_matrix_builtin_sm_full_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\clearpage
\input{result_matrix_external_sm_lc_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\clearpage
\input{result_matrix_external_sm_nlc_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\clearpage
\input{result_matrix_external_sm_full_table.tex}
\ReportMatrixLegend
\ReportLandscapeFooter
\end{landscape}
\clearpage
\pagestyle{empty}
\begin{landscape}
\section{Z-plus-Jets Evaluator Ladders}

The dedicated $d\bar d\to Z+(n-1)g$ ladders compare the independent reference
with JIT level 1, JIT level 3, ASM O3, and C++ O3 evaluator configurations. They retain
final-state multiplicities $n=1,\ldots,9$ for the built-in model and
$n=1,\ldots,6$ for the UFO-SM campaign. Each row states its evaluator backend
and optimization level explicitly; all other workload settings follow the
benchmark contract above.

Runtime comparisons between these backends also include their present
vectorization strategy. The SymJIT application evaluates a batch with SIMD
across phase-space points, whereas the current generated ASM and C++ payloads
are scalar and Rusticol invokes them point by point. Their ratios therefore
measure both symbolic/code-generation quality and this SIMD advantage; they
must not be interpreted as a comparison of otherwise identical vectorized
kernels.

\subsection*{Worked \(d\bar d\to Zg\) example}

For \(n=2\), the explicit process is
\[
  d(p_1)\,\bar d(p_2)\to Z(p_3)\,g(p_4).
\]
The report labels source particles in process order. The selected leading-colour
reference order for the selected-flow timing is therefore \((2,4,1,3)\): the
colour line enters through \(\bar d\), traverses the gluon, and exits through
\(d\), while the colour-singlet \(Z\) remains in the public ordering only to
keep source labels unambiguous. Internally, the colour-sector match is the
coloured word \((2,4,1)\).

\PAC{} builds one shared-current DAG for the selected process. Source nodes
carry particle, momentum, helicity, flavour, and colour-flow labels; composite
nodes are keyed by the full current identity and the external-label mask. When
two diagrams need the same current, the DAG contains one node and downstream
amplitude roots reuse its value. In the selected-flow/helicity-sum workload the
generator keeps the colour sector compatible with \((2,4,1)\) and sums source
helicities. In the all-flows/fixed-helicity workload it keeps all LC colour
flows but fixes one DAG-supported source-helicity assignment. The generated
artifact serializes the stages and evaluator payloads; Rusticol loads that
artifact, executes \texttt{Runtime.evaluate()} inside the native core, and
\texttt{BenchmarkRunner} records both the native repeated wall time and the sum
of evaluator-call timings.

\input{result_z_builtin_sm_table.tex}
\clearpage
\input{result_z_external_sm_table.tex}
\ReportLadderLegend
\ReportLandscapeFooter
\end{landscape}
\clearpage
\pagestyle{fancy}

\section{Colour-Singlet Model Ladders}

The scalar-contact ladder retains $n=2,\ldots,8$ final scalars. It tests generic
high-valence contact decomposition, identical-particle normalization, and
source parity without Standard-Model-specific kernels. The scalar-gravity
ladder retains $n=2,\ldots,4$ final gravitons and exercises spin-two
wavefunctions, tensor propagators, and momentum-dependent vertices. Since all
external particles in these fixtures are colour singlets, LC, NLC, and full
colour reduce to the same unit colour contraction.

For these ladders, the relative-difference row is
\(|M_{\mathrm{f64}}-M_{\mathrm{hp}}|/\max(|M_{\mathrm{hp}}|,10^{-300})\),
where \(M_{\mathrm{hp}}\) is the same point re-evaluated through the
higher-precision diagnostic path. It is a numerical stability check, not a
performance ratio.

\input{result_scalar_contact_table.tex}
\input{result_scalar_gravity_table.tex}

\section{Interpretation}

This report establishes coverage, methodology, and the current measured result
set. Performance comparisons are meaningful only for a reviewed baseline
produced from the same effective configuration on named hardware. Readers
should treat every \ReportNA{} entry as unavailable and should not interpolate,
copy, or estimate a value from neighbouring multiplicities or model profiles.

The retained measurement records under \texttt{docs/results/} are authoritative
for table completeness and provenance. The TeX inputs and this PDF are their
publication presentation.

\clearpage
\input{section_zgg_example.tex}
\clearpage
\input{section_zgg_dag.tex}
\clearpage
\input{section_ufo_support.tex}

\end{document}
