% SPDX-License-Identifier: 0BSD
\section{\texorpdfstring{The \(d\bar d\to Zgg\) DAG and Rusticol}{The d dbar -> Z g g DAG and Rusticol}}
\label{sec:zgg-dag}

The previous section described the physics graph.  This section gives the
exact mapping from that graph to compiled multi-output evaluators and then to
the Rusticol runtime.  The main invariant is simple: generation owns physics
identity and symbolic lowering; Rusticol owns a validated numerical schedule
of slots, stages, roots, and reductions.

\subsection{What identifies a current?}

The immutable \texttt{CurrentIndex} key is defined in
\path{src/pyamplicol/generation/dag_types.py}.  Two contributions share a
current if and only if every field in
\begin{equation}
 \Omega(J)=\bigl(
 t,\ m_I,\ I,\ H,\ \chi,\ s,\ F,\ Q,\ C,\ m_p,\ O,\ a,\ \pi_I
 \bigr)
 \label{eq:zgg-current-key}
\end{equation}
is equal.  There is no process-family or diagram label in this key.

\begin{center}
\footnotesize
\begin{tabular}{@{}L{1.48in}L{1.25in}L{3.90in}@{}}
\toprule
\textbf{field} & \textbf{example} & \textbf{role} \\
\midrule
\texttt{particle\_id} $t$ & $1$ & off-shell particle carried by the current \\
\texttt{external\_mask} $m_I$ & $26$ & bit mask of source subset $I=\{2,4,5\}$ \\
\texttt{external\_labels} $I$ & $(2,4,5)$ & sorted, unordered source-label set \\
\texttt{helicity\_ancestry} $H$ & source-state bit set & exact one-leg state choices feeding the current \\
\texttt{chirality} $\chi$ & $+1$ or $-1$ & Weyl-flow branch when applicable \\
\texttt{spin\_state} $s$ & scalar or tuple & local spin/polarization state beyond chirality \\
\texttt{flavour\_flow} $F$ & model tuple & conserved flavour-line identity \\
\texttt{quantum\_number\_flow} $Q$ & name/expression pairs & exact model-derived additive charges \\
\texttt{color\_state} $C$ & LC state & accuracy, internal sector, line groups, and basis keys \\
\texttt{momentum\_mask} $m_p$ & $26$ & momentum slot used by kernels and propagator \\
\texttt{coupling\_orders} $O$ & \texttt{QCD=2} & accumulated perturbative order envelope \\
\texttt{auxiliary\_kind} $a$ & \texttt{None} & proof-backed contact-decomposition species, if present \\
\texttt{ordered\_external\_labels} $\pi_I$ & $(2,5,4)$ & colour-sensitive traversal within the same subset \\
\bottomrule
\end{tabular}
\end{center}

Both the unordered labels and their order are intentional: the former fixes
the momentum and subset, while the latter prevents two colour-ordered currents
from being merged incorrectly.  Conversely, exact equality permits reuse
across every diagram and amplitude root that reaches the same state.  The
\texttt{\_CurrentTable.add\_or\_get()} operation in
\path{src/pyamplicol/generation/dag_table.py} is the sole identity-deduplication
point.  The resulting \texttt{current\_id} is only the dense array index of
that canonical node.

LC generation adds a second, complementary reuse mechanism.  Internal
currents are built in a shared-ordering state and their ordered labels and
basis keys record which flow segments they can serve.  Physical sector IDs are
restored only when a colour line closes into an amplitude root.  The two roots
in Eq.~\eqref{eq:zgg-physical-flows} therefore share sources, electroweak
subcurrents, the $J_g(4,5)$ family, and every other exactly equal current,
instead of cloning a complete recursion per flow.

Each one-leg state receives its own bit when sources are constructed; composing
currents takes the bitwise OR.  Thus $H$ identifies concrete source-state
choices, rather than merely the set of external labels.

Finally, \texttt{evaluation\_group\_id} addresses reuse that current identity
alone cannot express.  If one verified kernel value contributes, possibly
with different scalar \texttt{evaluation\_factor}s, to several target
currents, the symbolic stage computes it once.  For the worked graph this
reduces 242 target attachments to 210 kernel evaluations.  These three notions
must remain distinct:
\begin{equation}
 \underbrace{\text{same current key}}_{\text{one stored node}},\qquad
 \underbrace{\text{same evaluation group}}_{\text{one symbolic kernel value}},\qquad
 \underbrace{\text{same physical flow}}_{\text{one public output axis member}}.
 \label{eq:zgg-three-identities}
\end{equation}

\subsection{Topological stages and value slots}

The compiler sweeps proper source subsets in increasing cardinality.  An
interaction whose result covers $k$ source labels belongs to recursion stage
$k$.  No evaluator can read a current from its own or a later stage, so the
schedule is acyclic by construction.  For this example,
\begin{equation}
 \boxed{11\ \text{sources}}
 \longrightarrow
 \boxed{|I|=2:\ 18}
 \longrightarrow
 \boxed{|I|=3:\ 40}
 \longrightarrow
 \boxed{|I|=4:\ 48}
 \longrightarrow
 \boxed{48\ \text{amplitude roots}} .
 \label{eq:zgg-stage-chain}
\end{equation}
For one concrete source-state path, the same schedule can be read as
\begin{align}
 E_2:\quad C_{21}&={\cal P}_{21}K_{10}(C_2,C_9),
 & C_{25}&={\cal P}_{25}K_{14}(C_7,C_9),
 \label{eq:zgg-e2-concrete}\\
 E_3:\quad C_{53}&={\cal P}_{53}\bigl[K_{66}(C_{21},C_7)
                         +K_{82}(C_2,C_{25})+\cdots\bigr],
 \label{eq:zgg-e3-concrete}\\
 E_4:\quad C_{69}&={\cal P}_{69}\bigl[K_{90}(C_{53},C_4)+\cdots\bigr],
 \label{eq:zgg-e4-concrete}\\
 E_{\rm root}:\quad {\cal A}_0&={\cal C}_0(C_{69},C_1).
 \label{eq:zgg-root-concrete}
\end{align}
Here $C_2$ is the label-2 quark source with helicity $-1$, $C_7$ and
$C_9$ are the negative-helicity gluon sources on labels 4 and 5, $C_4$ is
the negative-helicity $Z$ source, and $C_1$ is the endpoint antiquark source.
The omitted terms are other admissible partitions contributing coherently to
the same target.  The subscripts on $K$ are evaluation-group IDs, not current
or interaction IDs.

\begin{lstlisting}
sources: C2=d(2,-), C7=g(4,-), C9=g(5,-), C4=Z(3,-), C1=dbar(1,+)
E2: I10: C2 + C9 -> C21 [G10]       I14: C7 + C9 -> C25 [G14]
E3: I66: C21 + C7 -> C53 [G66]      I83: C2 + C25 -> C53 [G82]
    I82: C2 + C25 -> C61 [G82]      (one kernel value, two targets)
E4: I98: C53 + C4 -> C69 [G90]
root: R0: contract(C69,C1) -> A0
\end{lstlisting}
This adjacency-list excerpt is diagnostic but exact for the current graph.
It also exposes why the namespaces cannot be conflated: $C_{53}$ is a
canonical current node, $I_{83}$ is one attachment to it, $G_{82}$ identifies
a reusable symbolic evaluation, and $R_0$ is an amplitude output.  Value-slot
IDs are a further runtime namespace assigning propagated or unpropagated
component storage to currents.  Internal LC sector IDs annotate root
construction; public IDs such as \texttt{flow:2,5,4,1} label the resolved
physics axis.

The stage records are assembled by
\texttt{build\_runtime\_schema()} in
\path{src/pyamplicol/generation/runtime_schema.py}.  They list input/output
current IDs, value-slot IDs, momentum slots, interaction IDs, and both
attachment and unique-evaluation counts.

A current and its stored value are not identical notions.  Depending on its
consumers, one current can have a \texttt{source}, \texttt{unpropagated}, or
\texttt{propagated} value slot.  Each slot owns a contiguous component range;
Weyl currents have two complex components and vector currents have four in the
worked model.  Keeping variants explicit prevents the runtime from silently
applying a propagator twice and lets the amplitude closure request precisely
the form it needs.

The complete schema for this graph has 256 complex value components, 13
four-vector momentum slots (52 real components), and 16 real model-parameter
slots.  A conceptual flattened state row therefore has
\begin{equation}
  x=\bigl[x_{\rm value}\mid x_{\rm momentum}\mid x_{\rm model}\bigr],
  \qquad |x|=256+52+16=324 .
  \label{eq:zgg-global-state}
\end{equation}
No compiled stage accepts all 324 entries.  Stage-local layout is mandatory:
for stage $k$, a map $L_k$ selects only the current components, momentum
components, and model parameters actually used there,
\begin{equation}
  x_k=L_k x,\qquad y_k=E_k(x_k),\qquad
  x[S_k]\mathrel{\leftarrow}y_k .
  \label{eq:zgg-stage-map}
\end{equation}
The construction is in
\path{src/pyamplicol/generation/stage_parameters.py}; Rusticol stores the same
local-to-global indices in the execution manifest.  Contiguous index runs are
precomputed, so most packing and output assignment becomes slice copies rather
than scalar lookup loops.

\subsection{What Symbolica and SymJIT compile}

\texttt{build\_generic\_stage\_compiler\_blueprint()} in
\path{src/pyamplicol/generation/stage_planning.py} creates one multi-output
symbolic blueprint per recursion stage and one for the amplitude roots.  For a
target current $j$, its output expression is
\begin{equation}
  y_j=\mathcal P_j\!\left[
       \sum_{e:\,\operatorname{target}(e)=j}
       f_e\,K_{g(e)}(x_k)
     \right],
  \label{eq:zgg-stage-expression}
\end{equation}
where $K_{g(e)}$ is cached by evaluation-group ID, $f_e$ is the attachment
factor, and $\mathcal P_j$ is the output propagator or identity.  Component
expressions, couplings, momentum dependence, and propagators come from the
selected model; the stage compiler does not know that this example contains a
$Z$ or a gluon.

Symbolica optimizes the whole multi-output expression of one stage: common
subexpressions, Horner schemes, and common-pair elimination can therefore
cross current-component boundaries inside that stage.  With the default JIT
backend, SymJIT O3 then compiles a batched complex-f64 application.  The direct
application capability is recorded as
\texttt{symjit.application.complex-f64.v1}; Rusticol can load and execute this
f64 payload without importing Symbolica.  Retained Symbolica evaluator state
is used for higher-precision Python requests.

Output chunking is a compilation boundary, not a physics boundary.  If a
stage has more than the configured 512 scalar outputs, it is split into
multi-output chunks sharing the same local input vector.  A fanout-aware
ordering in \path{src/pyamplicol/generation/stage_planning.py} places outputs
with common evaluation groups near one another, reducing duplicated work when
a group would otherwise cross chunk boundaries.  At runtime the local input is
packed once per stage and batch, each compiled chunk consumes that same packed
buffer, and the concatenated outputs are scattered to their recorded slots.
Dependencies are still cut only between recursion stages.

Compiled generation streams these stages.  Once a blueprint has been compiled
and written, its Symbolica expressions can be released before the next stage
is built.  This bounds peak expression memory without changing the DAG or the
runtime schedule.  The relevant writer path is
\path{src/pyamplicol/generation/stage_artifacts.py}, while backend settings and
payload construction live in
\path{src/pyamplicol/evaluators/symbolica_compile.py}.

\subsection{Artifact records and Rusticol execution}

For the compiled route described in this section, the root
\texttt{artifact.json} is a process-artifact schema-v3 manifest.  It
binds global model/configuration data and payload hashes to process-local
records.  The files relevant to one concrete process are:

\begin{center}
\small
\begin{tabular}{@{}L{2.40in}L{4.22in}@{}}
\toprule
\textbf{record} & \textbf{runtime meaning} \\
\midrule
\path{processes/evaluators.json} & evaluator capabilities and payload locations \\
\path{processes/<id>/execution.json} & value/momentum/model layout, sources,
  ordered stages, chunks, roots, and reduction schedule \\
\path{processes/<id>/physics.json} & external particles, physical helicity and
  flow IDs, coverage, symmetry expansion, selectors, and normalization \\
evaluator applications/libraries & target-specific compiled numerical kernels \\
\path{API/} & validation point and Python, Rust, C++, and Fortran examples \\
\bottomrule
\end{tabular}
\end{center}

The complete \texttt{CurrentIndex} is a generation contract.  The execution
projection serializes only the fields needed to validate and run its slots;
ordered-label proofs and other generation-only evidence need not burden the
hot runtime.  By contrast, physical helicity and flow metadata remains explicit
because it defines the public resolved axes and selector semantics.

\begin{samepage}
Rusticol's f64 path is implemented in
\path{rust/crates/rusticol-core/src/engine/evaluation.rs}.  For a batch of
points, one execution is:
\begin{enumerate}
  \item reuse and clear the state scratch buffer;
  \item fill source wavefunctions in their source value slots;
  \item form all recorded all-outgoing momentum sums and copy current model
        parameter values into the global state;
  \item for every recursion stage, pack $x_k$, call all evaluator chunks,
        and assign $y_k$ to the global value slots;
  \item pack and call the amplitude-root evaluator;
  \item sum roots coherently, contract colour, expand exact physical symmetry
        representatives when resolved output is requested, and apply
        normalization.
\end{enumerate}
\end{samepage}
The stage and amplitude implementations reuse their parameter and output
scratch buffers across calls.  The global model-parameter vector is mutable at
runtime; an atomic update validates all supplied values, refreshes derived
parameters and masses, and recomputes the factor in
Eq.~\eqref{eq:zgg-normalization}.  No mass, width, or coupling is baked into
the orchestration schedule merely because it is constant in one run card.

For LC resolved evaluation, the public tensor has shape
\begin{equation}
  R_{n,h,c}=|{\cal M}_{h,c}(p_n)|^2,
  \qquad
  \operatorname{shape}(R)=
  (N_{\rm point},N_{\rm helicity},N_{\rm flow}) .
  \label{eq:zgg-resolved-shape}
\end{equation}
For this process the final two dimensions have lengths 48 and 2.  Structural
zeros occupy their declared entries.  \texttt{evaluate\_resolved()} can select
stable helicity/flow IDs and materializes these components; its
\texttt{total()} is their explicit sum.  \texttt{evaluate()} follows the
optimized summed path directly and need not allocate the resolved tensor.
Neither interface exposes internal current, slot, or sector IDs.

\subsection{The two runtime timing boundaries}

The profiler deliberately distinguishes orchestration from compiled evaluator
calls.  Its reported f64 wall sample starts in the native Rusticol method after
the caller-language buffer conversion and repeatedly executes the ordinary
core path through final reduction.  It therefore includes Rust-side input
batch preparation, source and momentum construction, stage-local packing,
chunk calls, output assignment, root packing/call, and reduction, but excludes
Python/NumPy, C++, Fortran, or Rust caller-side packing.

The evaluator sum is narrower:
\begin{equation}
 t_{\rm eval}=\sum_{k}t\bigl(E_k\bigr)+t\bigl(E_{\rm root}\bigr),
 \qquad
 t_{\rm core}=t_{\rm eval}+t_{\rm source}+t_{\rm momentum/model}
 +t_{\rm pack}+t_{\rm assign}+t_{\rm reduce}+t_{\rm batch} .
 \label{eq:zgg-timing-boundary}
\end{equation}

\begin{center}
\small
\begin{tabular}{@{}L{2.78in}L{3.84in}@{}}
\toprule
\textbf{provenance marker} & \textbf{quantity} \\
\midrule
\path{runtime_core_repeated_wall_time} & native repeated total path,
  normalized per point; common metric for all language APIs \\
\path{runtime_profile_core_evaluator_call_time} & sum of recursion-stage
  and amplitude-root evaluator call times only \\
native component profile & source fill, momentum/model setup, per-stage input
  pack, evaluator call and output assignment, root pack/call, and reduction \\
\bottomrule
\end{tabular}
\end{center}

These boundaries make a wall/evaluator difference interpretable as work inside
Rusticol rather than Python probing overhead.  They also make Python, Rust,
C++, and Fortran measurements comparable when they call the same f64 artifact.
The CLI calibration, uncertainty estimate, progress display, and interruptible
sampling policy are implemented in \path{src/pyamplicol/benchmarking.py}; the
native timers themselves are in
\path{rust/crates/rusticol-core/src/engine/native_runtime.rs} and
\path{rust/crates/rusticol-core/src/engine/evaluation.rs}.
