% SPDX-License-Identifier: 0BSD
\section{Arbitrary UFO and Serialized-JSON Models}
\label{sec:ufo-support}

The external-model path is a compiler, not a permissive UFO interpreter.  It
accepts a trusted UFO Python module or its serialized JSON representation,
normalizes the model to a typed, model-independent intermediate
representation, and only then exposes interactions to the current-recursion
generator.  A structure is executable when the compiler can construct its
component expressions and prove every transformation used to lower or reuse
them.  Failure to prove a useful optimization merely disables that
optimization; failure to prove a transformation required for correctness
rejects the model with a structured diagnostic.

This section describes the implemented contract.  The handwritten Standard
Model in \path{src/pyamplicol/models/builtin/} is deliberately outside that
contract: \texttt{BuiltinSM}\allowbreak\texttt{Model} may use SM-specific
formulae, while \texttt{CompiledUFO}\allowbreak\texttt{Model} must derive its
decisions from particle metadata,
normalized tensors, propagators, couplings, and exact algebra.  The boundary
forbids SM PDG classifiers and built-in implementation symbols from leaking
into the external-model modules.

\subsection{One route from UFO and JSON to an executable model}

The public entry point \texttt{compile\_model\_source()} in
\path{src/pyamplicol/models/loading.py} recognizes a UFO directory, a JSON
model, an already compiled model, or the special built-in model.  For an
external source it lazily invokes \texttt{ufo-model-loader}.  Both source forms
therefore enter the same route:
\begin{equation}
  \begin{aligned}
    \{\text{UFO directory},\text{ serialized JSON}\}
      &\xrightarrow{\ \texttt{load\_model}\ }
        \texttt{ufo-model-loader.Model}\\
      &\xrightarrow{\ \text{compact serialization and compilation}\ }
        \texttt{CompiledModelIR}.
  \end{aligned}
  \label{eq:ufo-loading-route}
\end{equation}
The UFO directory is executable Python and must therefore be trusted.  The
JSON form is data-only and is the portable form to archive or exchange.

The loader is first called with wrapped Lorentz indices disabled.  This lets
\texttt{\_classify\_external\_propagators()} compare a model-supplied
propagator against the loader's exact default Feynman-gauge candidates.
Indices are then wrapped and the model is serialized with
\texttt{JSONLook.COMPACT}.  Consequently, UFO and JSON inputs do not maintain
separate physics implementations after loading.

Every source symbol is put in a model-local namespace by
\path{src/pyamplicol/_internal/physics/symbols.py}.  A model called
\texttt{sm} uses heads such as
\(\texttt{model\_sm::GC\_1}\), while compiler-owned currents, momenta, dummy
indices, and derived couplings use the \texttt{pyamplicol::} namespace.  The
registry rewrites the loader's temporary \texttt{UFO::} heads; a compiled
\texttt{CompiledModelIR} is rejected if an executable expression still
contains a process-global \texttt{UFO::} symbol.  Two loaded models can thus
coexist without silently identifying equally named parameters or tensors.

The canonical IR in \path{src/pyamplicol/models/contracts.py} contains typed
records for particles, parameters, coupling orders, propagators, vertex terms,
oriented trivalent kernels, direct and closure contractions, tensor and
current orderings, and Goldstone partners.  It is not a bag of strings.  On
reload it checks the model-schema version, compiler version and fingerprint,
proof identities, tensor-ordering links, and required fields before any DAG is
built.  The compiler fingerprint includes the pyAmpliCol, Symbolica, and
\texttt{ufo-model-loader} versions and the relevant serialization and
lowering policies; a stale compiled model is regenerated rather than guessed
compatible.

\begingroup
\footnotesize
\begin{longtable}{@{}L{1.25in}L{2.05in}L{3.35in}@{}}
\toprule
\textbf{compiler stage} & \textbf{resulting contract} & \textbf{implementation} \\
\midrule
\endfirsthead
\toprule
\textbf{compiler stage} & \textbf{resulting contract} & \textbf{implementation} \\
\midrule
\endhead
source loading & one compact loader-model payload &
  \path{models/loading.py}: \texttt{\_load\_external\_model()} and
  \texttt{preflight\_model()} \\
parameter resolution & namespaced external and derived expressions &
  \path{models/compiler_records.py} and
  \texttt{ModelSymbolRegistry} \\
tensor normalization & canonical colour and Lorentz expressions &
  \path{models/tensors.py}, using idenso, Spenso, and Symbolica \\
kernel construction & oriented trivalent contracts and contact auxiliaries &
  \path{models/compiler_entry.py}, \path{models/compiler_kernels.py},
  \path{models/compiler_contacts.py} \\
ordering construction & explicit source axes, Weyl projections, and current
  embeddings & \path{models/compiler_tensor_ordering.py} \\
model-owned closure & propagators, direct/closure contractions, and Goldstone
  policy & \path{models/compiler_contractions.py},
  \path{models/compiler_gauge.py} \\
optimization proofs & kernel equivalence, colour-flow auxiliaries, and exact
  model symmetries & \path{models/compiler_color_flow.py} and
  \path{models/external_symmetries.py} \\
\bottomrule
\end{longtable}
\endgroup

\subsection{From a UFO vertex to concrete current kernels}

A UFO vertex is a matrix over colour and Lorentz structures.  The compiler
expands it into separate terms
\begin{equation}
  \mathcal V(1,\ldots,n)
  = \sum_{a,b} g_{ab}\,
    C_a(c_1,\ldots,c_n)\,
    L_b(s_1,p_1;\ldots;s_n,p_n),
  \label{eq:ufo-vertex-matrix}
\end{equation}
and stores the original sources together with their normalized forms and the
coupling-order vector of \(g_{ab}\).  The normalization in
\path{src/pyamplicol/models/tensors.py} converts wrapped UFO heads to typed
Spenso expressions.  It applies idenso's \texttt{simplify\_metrics},
\texttt{simplify\_gamma}, and \texttt{simplify\_color}; Spenso then
materializes dense tensor components in a declared Cartesian order.  Residual
UFO tensor heads, indeterminate expressions, duplicate coordinates, or missing
dense coordinates are errors.

The normalized Lorentz basis includes scalars, momenta, metrics,
Dirac identity and gamma matrices, \(\gamma_5\), chiral projectors, slashed
momenta, and sigma tensors.  The supported colour representations are the
SU(3) singlet, fundamental, antifundamental, and adjoint.  Exact trilinear
projection recognizes four executable colour families:
\begin{equation}
  1,\qquad
  \delta_i{}^{\bar\jmath},\qquad
  (T^a)_i{}^{\bar\jmath},\qquad
  f^{abc}.
  \label{eq:trilinear-color-basis}
\end{equation}
For a proposed basis tensor \(B_\sigma\), projection succeeds only when the
normalized tensor obeys the componentwise identity
\begin{equation}
  C_a(\boldsymbol c)=\kappa_a B_\sigma(\boldsymbol c)
  \quad\text{for every materialized colour component }\boldsymbol c,
  \label{eq:exact-color-projection}
\end{equation}
with an exact scalar \(\kappa_a\).  Numerical projection exists as a diagnostic
but does not certify an executable kernel.  The symmetric adjoint invariant
\(d^{abc}\), for example, can be recognized diagnostically but is not in the
current executable trilinear colour basis.

For a trilinear term, \texttt{\_compile\_oriented\_kernels()} chooses each
distinct result species and both nonidentical input orders.  Spenso contracts
the normalized tensor with formal left and right currents and physical
momenta.  The resulting component contract has the schematic form
\begin{equation}
  K^{A_r}_{r\leftarrow ij}(J_i,J_j)
  =g_{a b}\,\kappa_a
    \sum_{A_i,A_j}
    L_b^{A_r}{}_{A_i A_j}(p_i,p_j,p_r)
    J_i^{A_i}J_j^{A_j},
  \qquad p_r=-(p_i+p_j),
  \label{eq:oriented-kernel}
\end{equation}
followed by the model-owned propagator when the result is an internal current.
The coupling, perturbative orders, runtime parameters, source-leg map, colour
normalization, and input/output ordering identifiers remain attached to the
kernel.  Weyl projection is therefore an explicit ordering/embedding contract,
not an inference made later from a particle name.

The compiler recognizes a compact Yang--Mills three-vector form only after its
components have been proved equal, up to one exact constant, to the dense
Spenso result.  This is an implementation optimization, not an alternative
physics formula.

\subsection{What a proof or certificate asserts}

The word \emph{proof} is used narrowly.  It is a reproducible algebraic
witness that an optimized or decomposed executable contract reconstructs the
normalized source contract.  It is not a statement that a model is physically
consistent, unitary, or gauge complete.  Three assurance mechanisms are
distinct:

\begin{enumerate}
  \item A \textbf{serialized decomposition proof} is attached to a four-point
        \texttt{CompiledVertexTerm}.  Its algorithm name and version, source
        identity, split topology, index map, component basis, signs, and
        multiplicities are revalidated when the compiled model is loaded.
  \item \textbf{Kernel-equivalence metadata} is written on oriented kernels.
        Fully lowered component expressions are compared under input exchange
        and an exact factor \(\eta=\pm1\).  Equal kernels receive one
        \texttt{evaluation\_class}, a representative input order, and a factor,
        so the DAG may evaluate the representative once and fan its value out.
  \item A \textbf{model-level symmetry certificate} is re-derived by
        \texttt{derive\_external\_symmetry\_}\allowbreak
        \texttt{certificates()} when a
        \texttt{CompiledUFOModel} is constructed.  It binds a theorem to
        digests of the compiled particle, propagator, ordering, vertex, and
        executable-kernel contracts.  It is not accepted as a free-form claim
        from the UFO source.
\end{enumerate}

For two kernel expressions \(K\) and \(K'\), reusable evaluation requires an
exact relation
\begin{equation}
  K'(x,y;p_x,p_y)
  =\eta\,K(y,x;p_y,p_x),
  \qquad \eta\in\{-1,+1\},
  \label{eq:kernel-equivalence}
\end{equation}
after resolving coupling aliases and canonicalizing all component expressions.
For a global theorem, the digest is
\begin{equation}
  D=\operatorname{SHA256}\!\left(
    \operatorname{canonicalJSON}
    \{\text{source},\text{propagator},\text{orderings},
      \text{terms},\text{kernels}\}\right).
  \label{eq:certificate-digest}
\end{equation}
The selectors and 64-character digests must be complete and mutually
consistent.  Renaming a contracted tensor dummy must not change \(D\), but a
different contraction graph must.  The internal helper
\begin{center}
  \texttt{\_canonical\_tensor\_product\_expressions()}
\end{center}
in \path{src/pyamplicol/models/external_symmetries.py} calls Symbolica's
\texttt{Expression.canonize\_tensors()} on the contracted Lorentz, colour, and
spinor indices.  Its reserved replacement head is
\begin{center}
  \texttt{pyamplicol::canonical\_tensor\_index}.
\end{center}
The certificate contract requires alpha-renaming invariance and
contraction-graph sensitivity.

The important fail-closed distinction is:
\begin{itemize}
  \item if a reflection or parity certificate is absent, the generator keeps
        both configurations and remains correct, but performs less reuse;
  \item if a four-point contact cannot be lowered without changing its tensor,
        colour, coupling, or multiplicity, generation stops rather than
        silently dropping or approximating that interaction.
\end{itemize}

\begingroup
\small
\begin{longtable}{@{}L{1.40in}L{2.20in}L{3.05in}@{}}
\toprule
\textbf{proof class} & \textbf{checked identity} & \textbf{optimization or lowering enabled} \\
\midrule
\endfirsthead
\toprule
\textbf{proof class} & \textbf{checked identity} & \textbf{optimization or lowering enabled} \\
\midrule
\endhead
trilinear colour projection & Eq.~\eqref{eq:exact-color-projection} in the
  supported SU(3) basis & colour-flow interpretation of an oriented kernel \\
kernel evaluation equivalence & Eq.~\eqref{eq:kernel-equivalence}, including
  coupling and ordering contracts & one evaluator value reused by
  symmetry-related current contributions \\
four-point contact decomposition & exact colour topology, open-axis Lorentz
  basis, orientation signs, and multiplicity & two trivalent auxiliary-current
  stages with no artificial pole \\
fundamental Fierz identity & exact \(T^a\) trilinear projection and eligible
  massless adjoint-vector metadata & compiler-owned singlet-subtraction
  auxiliary for LC flow \\
vectorlike parity & exact fundamental-generator colour and gamma-current
  Lorentz tensor & global helicity-flip representative reuse \\
Yang--Mills cubic/quartic sector & exact \(f^{abc}\), three-vector tensor,
  quartic basis, coupling relation, and closed reachable sector & pure-adjoint
  helicity-zero theorem and LC trace-reflection folding \\
local adjoint reflection & every relevant cubic kernel is antisymmetric under
  left/right exchange & current reflection phase reuse \\
Goldstone partner contract & quantum numbers, exact mass expression,
  uniqueness, and propagator policy & unitary-gauge absorption or explicit
  model-supplied Goldstone treatment \\
tensor/current ordering & explicit physical axes and component permutations &
  stable Spenso-to-current and Weyl component maps \\
\bottomrule
\end{longtable}
\endgroup

\subsection{Four-point contacts: exact auxiliary-current factorization}

Every momentum-independent valence-four term receives a
\texttt{CompiledContactDecompositionProof} before lowering.  The serialized
algorithm is \texttt{ufo-four-point-contact-decomposition}, version 2.  A proof
has status \texttt{proven} or \texttt{unsupported}; its identity includes the
term and vertex identifiers, particle tuple, colour and Lorentz matrix
indices, original sources, and normalized expressions.  A stale version or an
identity mismatch is rejected.

The record family is explicit:
\begin{itemize}
  \item \texttt{CompiledContactDecompositionProof} owns the term identity and
        all proved result-leg splits;
  \item \texttt{CompiledContactDecompositionSplit} and
        \texttt{CompiledContactDummyIndexMapping} describe one topology and
        its shared colour index;
  \item \texttt{CompiledContactOrientationProof} fixes every input order and
        sign; and
  \item \texttt{CompiledContactUnsupportedReason} carries a stable failure
        code and context.
\end{itemize}

Two decomposition kinds are implemented.

\paragraph{Literal colour singlet.}
If all four legs are colour singlets and \(C=1\), the Lorentz tensor may be
split directly.  A literal singlet attached to any coloured leg is not treated
as an implicit contraction; it fails with
\texttt{literal-singlet-}\allowbreak\texttt{with-colored-legs}.

\paragraph{Product of two structure constants.}
The coloured gauge-contact path requires exactly
\begin{equation}
  C^{a_1a_2a_3a_4}
  = c\,f^{a_i a_j b}f^{b a_k a_r},
  \label{eq:two-f-color}
\end{equation}
up to exact permutations, with one and only one shared adjoint dummy \(b\) and
a scalar prefactor \(c\).  For each possible result leg \(r\), the compiler
records the paired legs \((i,j)\), remaining leg \(k\), dummy-index map,
permutation parity, LC normalization powers, and the exact scalar coefficient.
It then introduces a non-propagating auxiliary current
\begin{align}
  A^{b}_{\rho\sigma}[i,j]
    &= f^{b a_i a_j}
       \sum_{A_i,A_j}
       P_{\rho\sigma;A_iA_j}
       J_i^{A_i}J_j^{A_j},
       \label{eq:contact-partial}\\
  J_r^{A_r}\big|_{V_4}
    &= \frac{c\,s_{ijkr}}{m_r}
       f^{a_r b a_k}
       \sum_{\rho,\sigma,A_k}
       F^{A_r}{}_{\rho\sigma A_k}
       A^{b}_{\rho\sigma}J_k^{A_k}.
       \label{eq:contact-final}
\end{align}
Here \(s_{ijkr}=\pm1\) is the recorded orientation parity and \(m_r\) is the
number of indistinguishable assignments of the remaining input species.  The
original coupling and complete perturbative-order vector occur only in
Eq.~\eqref{eq:contact-final}; Eq.~\eqref{eq:contact-partial} has unit coupling
and no propagator.  The factorization therefore introduces neither an
unphysical pole nor a duplicated coupling/order weight.

The Lorentz split is not inferred from the phrase ``four-gluon vertex.''  Spenso first
contracts the chosen input pair while leaving the result and remaining-leg
axes open.  \texttt{\_compress\_contact\_components()} stores a basis of
distinct components and reconstructs every omitted component by an exact
zero or \(\pm1\) map.  The final kernel contracts that basis and must reproduce
the source tensor component by component.  This same mechanism covers an
SU(3) four-vector term such as the four-gluon vertex and colour-singlet
electroweak-like four-vector contacts built from metric tensors.  What differs
is the colour proof: \texttt{two-structure-constants} for the former and
\texttt{literal-color-singlet} for the latter.

The compiler deduplicates identical contact partials and fuses compatible
finals after proof validation.  Unsupported diagnostics distinguish an
incorrect topology from a missing feature: wrong factor count, malformed
structure-constant indices, non-scalar colour prefactor, non-unique shared
dummy, absent result leg, and a nontrivalent structure-constant topology all
have separate reason codes in
\path{src/pyamplicol/models/compiler_contacts.py}.

\subsection{Arbitrary-valence colour-singlet contact trees}

Colour-singlet contacts with valence \(n\geq4\) are lowered by
\texttt{\_compile\_color\_singlet\_contact\_trees()} in
\path{src/pyamplicol/models/compiler_contact_trees.py}.  The already proved
momentum-independent four-point case uses the preceding path; other singlet
contacts are split recursively at the midpoint into a balanced binary tree.
For a set of input leaves \(S\), the generic recursion is
\begin{equation}
  A_S=\Phi_S(A_{S_L},A_{S_R}),
  \qquad S=S_L\mathbin{\dot\cup}S_R,
  \qquad
  J_r\big|_{V_n}=\frac{g}{m_r}
      \Psi_r(A_{S_L},A_{S_R}),
  \label{eq:contact-tree}
\end{equation}
where the internal \(A_S\) are non-propagating, \(g\) and its coupling orders
appear only in the final map \(\Psi_r\), and \(m_r\) removes identical-input
assignment multiplicity.  A balanced tree has \(O(n)\) auxiliary operations
and \(O(\log n)\) depth.

For an all-scalar contact, each auxiliary carries one component and
\(\Phi_S(x,y)=xy\).  This is the path exercised by the arbitrary-valence
scalar-contact model.  For non-scalar or momentum-dependent singlet contacts,
an auxiliary carries the current components and four-momentum of every
physical leaf below it.  At the final node, the original normalized
\(n\)-point Lorentz expression is reconstructed with
\begin{equation}
  p_r=-\sum_{i\ne r}p_i.
  \label{eq:contact-momentum-conservation}
\end{equation}
On Linux, very large dense contractions are evaluated in bounded stages when
the direct input work exceeds 1024 components; each staged group is limited to
256 input components and its intermediate tensor is materialized before the
next contraction.  This changes only contraction order.  The direct function
\path{eager_color_singlet_vertex_term_components()} remains the
component oracle for the tree result.

This is deliberately not advertised as an arbitrary coloured \(n\)-point
algorithm.  It is generic in valence, spin, momentum dependence, and Lorentz
expression only after the colour tensor has been proved to be a singlet that
requires no unresolved coloured internal channel.

\subsection{Colour-flow and model-level symmetry proofs}

The LC compiler derives its singlet-subtraction channel from the fundamental
Fierz identity
\begin{equation}
  (T^a)_i{}^{\bar\jmath}(T^a)_k{}^{\bar l}
  =T_R\left(
    \delta_i{}^{\bar l}\delta_k{}^{\bar\jmath}
    -\frac{1}{N_c}
     \delta_i{}^{\bar\jmath}\delta_k{}^{\bar l}
  \right).
  \label{eq:fierz}
\end{equation}
The compiler function
\begin{center}
  \texttt{synthesize\_fundamental\_fierz\_auxiliaries()}
\end{center}
in
\path{src/pyamplicol/models/compiler_color_flow.py} is enabled only for an
exactly projected \(T^a\) trilinear with fundamental fermion lines and a
self-conjugate, massless adjoint vector with a standard propagator.  It creates
one compiler-owned colour-singlet vector auxiliary and reuses the proved
Lorentz and coupling kernel.  The \(1/N_c\) closure coefficient is attached in
one canonical orientation.  No gluon name or PDG code participates.

Four further exact recognizers in
\path{src/pyamplicol/models/external_symmetries.py} recover the reusable
structure normally associated with a gauge theory:
\begin{itemize}
  \item A \textbf{vectorlike parity kernel} has one massless adjoint vector,
        a fundamental/antifundamental fermion pair, exact \(T^a\) colour, and a
        Lorentz tensor that is a constant multiple of the gamma-current
        reference.  Chiral-projector deformations do not pass this proof.
  \item A \textbf{Yang--Mills cubic kernel} has one self-conjugate massless
        adjoint-vector species, a standard propagator, exact \(f^{abc}\), and
        the three-vector Lorentz tensor up to an exact constant.  The effective
        cubic coupling is retained symbolically.
  \item A \textbf{Yang--Mills quartic group} must uniquely span the three
        \(ff\times gg\) basis elements of the four-vector vertex, and each
        coefficient must obey the exact relation to the square of the cubic
        coupling.  Recognizing three individually familiar-looking terms is
        insufficient if the coupling relation fails.
  \item A \textbf{local adjoint-current reflection} requires every relevant
        cubic kernel to satisfy Eq.~\eqref{eq:kernel-equivalence} with
        \(\eta=-1\), exact \(f^{abc}\), and a standard propagator.
\end{itemize}

A global Yang--Mills theorem is emitted only if the reachable trivalent
compiled sector is closed: starting from the candidate adjoint source, every
kernel reachable from two already reachable currents must itself be certified
Yang--Mills.  Contact auxiliaries are included in this traversal.  One extra
reachable non-Yang--Mills interaction therefore disables the global theorem
rather than being ignored.  A complete certificate enables the pure-adjoint
helicity-zero theorem, global helicity-flip representatives, LC trace
reflection, and shared single-trace basis.  The ordinary DAG remains complete
when the certificate is absent.

These generic proofs recover the built-in-SM current topology for the
established UFO-SM validation matrix without assuming that every external model
must do so.  Validation covers electroweak, QCD, top, pure-gluon,
charged-current, multi-boson, and up to three-quark-line examples.  Equivalent
built-in and UFO-SM models must have equal minimal coupling limits and equal
current, interaction, amplitude-root, and colour-sector counts; exact kernel
reuse may reduce evaluator calls but may not increase them.  The same proof is
invariant under arbitrary particle-name, PDG, and inventory-order changes.
This establishes the certified classes, not a universal topology theorem for
all UFO syntax.

\subsection{Propagators, closures, Goldstones, and spin two}

Propagators are model contracts rather than hard-coded particle identities.
For standard scalar, Dirac, vector, and spin-two records, the evaluator in
\path{src/pyamplicol/models/external_evaluation.py} implements the expected
runtime-mass and runtime-width kernels, schematically
\begin{align}
  P_0(p)&=\frac{i}{p^2-m^2+i m\Gamma},
  &P_{1/2}(p)&=\frac{i(\gamma^\mu p_\mu+m)}{p^2-m^2+i m\Gamma},
  \label{eq:standard-propagators-a}\\
  P_1^{\mu\nu}(p)&=
    \frac{-i}{p^2-m^2+i m\Gamma}
    \left(g^{\mu\nu}-\frac{p^\mu p^\nu}{m^2}\right),
  &P_2^{\mu\nu,\rho\sigma}(p)&=
    \frac{i\,\Pi^{\mu\nu,\rho\sigma}(p)}
         {p^2-m^2+i m\Gamma}.
  \label{eq:standard-propagators-b}
\end{align}
The massless-vector branch is Feynman gauge and does not use the singular
\(p^\mu p^\nu/m^2\) term.  Weyl currents use explicit chirality projections.
For spin two, \(\Pi\) is the de Donder massless or Fierz--Pauli massive
projector represented in a 16-component ordered tensor space.  Synthetic
contact auxiliaries have the identity map and no propagator; the Fierz
singlet-subtraction auxiliary propagates as its compiler-owned massless vector.

A custom UFO propagator is accepted when its normalized numerator and
denominator can be materialized through the same Spenso ordering contract.  It
is applied exactly and is not silently converted to a preferred gauge.  Its
presence intentionally disables symmetry theorems that require the standard
propagator.

\texttt{compile\_contraction\_records()} emits explicit scalar, Dirac, opposite
Weyl-chirality, mostly-minus vector, and rank-two tensor-product-metric
contractions.  Rusticol consumes these records and does not infer a closure
from component count.  Goldstone matching in
\texttt{compile\_goldstone\_partner\_records()} similarly uses quantum-number
flow and the exact resolved mass expression.  A unique massive vector with a
default propagator absorbs its Goldstone in the unitary-gauge path; a custom
vector propagator retains the model-supplied Goldstone.  Ambiguous matches
fail closed.

UFO spin code 5 is therefore a real current type, not a special-case scalar:
it has two ordered Lorentz axes, 16 components, tensor-product closure, and a
spin-two propagator.  The packaged massless scalar-gravity model validates the
generic tensor route, including axis relabelling and transposed source storage.
Massive spin two is accepted with an explicit experimental warning; arbitrary
massive spin-two phenomenology is not yet a qualified release capability.

\subsection{Implemented support boundary}

The support matrix below separates implemented current capabilities from
unsupported classes.  ``Proof-gated'' means that qualifying models work
without an SM-specific exception; it does not mean every algebraically
equivalent UFO spelling is already recognized.

\begingroup
\small
\setlength{\LTpre}{0.3em}
\setlength{\LTpost}{0.3em}
\begin{longtable}{@{}L{0.83in}L{1.47in}L{0.93in}L{3.15in}@{}}
\toprule
\textbf{area} & \textbf{class} & \textbf{status} & \textbf{exact boundary} \\
\midrule
\endfirsthead
\toprule
\textbf{area} & \textbf{class} & \textbf{status} & \textbf{exact boundary} \\
\midrule
\endhead
source & UFO directory / JSON & supported & both lower through one loader-model
  payload; UFO Python must be trusted \\
spin & scalar, Dirac, vector & supported & standard wavefunctions,
  propagators, current orderings, and closures \\
spin & massless spin two & supported & 16-component tensor path tested by the
  packaged scalar-gravity model \\
spin & massive spin two & experimental & Fierz--Pauli path exists, but broad
  model validation is incomplete \\
spin & UFO ghosts & partial & one-component metadata and ordering exist;
  propagating ghosts require an exactly lowerable custom propagator and are
  not broadly qualified \\
spin & Majorana/FNV, spin $3/2$ & unsupported & no fermion-number-violating
  flow or Rarita--Schwinger current contract \\
colour & $1,3,\bar3,8$ of SU(3) & supported & LC and current contracted NLC/full
  basis \\
colour & $6,\bar6$, extra groups & unsupported & no sextet or multi-group
  flow/contraction representation \\
arity 3 & $1,\delta,T,f$ colour & supported & exact projection plus generic
  materializable Lorentz components \\
arity 3 & $d^{abc}$, $\epsilon$, $K_6$, $T_6$ & unsupported & recognized or
  known source heads are not sufficient to construct an executable colour
  contract \\
arity 4 & colour singlet & supported & momentum-independent proof path;
  generic singlet-tree path for other materializable tensors \\
arity 4 & two-$f$ gauge colour & proof-gated & one shared adjoint dummy,
  trivalent topology, scalar prefactor, exact Lorentz reconstruction \\
arity 4 & other coloured tensors & unsupported & no certified auxiliary colour
  channel \\
arity $>4$ & colour-singlet contact & supported & balanced no-pole tree;
  original coupling/order only at final node \\
arity $>4$ & coloured contact & unsupported & no general irreducible-channel
  factorization proof \\
Lorentz & idenso/Spenso basis & supported & all source tensor heads must
  normalize and materialize with explicit axes \\
Lorentz & form factors / unknown functions & unsupported & no executable and
  serializable function contract \\
propagator & standard $0,\frac12,1,2$ & supported & runtime mass/width and
  explicit ordering/closure \\
propagator & custom UFO tensor & proof-gated & exact Spenso lowering; gauge
  conversion and affected symmetry reuse are disabled \\
symmetry & vectorlike/Yang--Mills/reflection & proof-gated & exact normalized
  identities and complete reachable-sector digest \\
\bottomrule
\end{longtable}
\endgroup

Preflight in \texttt{preflight\_model()} rejects unsupported spin or colour
codes, Majorana fermions, form factors, wrong known-function arities, and
unknown expression functions before expensive compilation.  Tensor
normalization and contact lowering impose the narrower executable boundary
after preflight.  Thus recognizing a UFO head such as \texttt{K6} during
syntax inspection does not imply that a sextet colour current can be built.

\subsection{Support boundary and extension requirements}

Support is defined by algebraic contracts rather than process-family or PDG
exceptions.  A new class requires a typed source representation and
normalization, an explicit component ordering and current embedding, a direct
contraction and colour-flow interpretation, and an exact proof of orientation
signs, coupling placement, multiplicities, and any evaluator reuse.  The proof
must remain invariant under dummy-index, source-label, and particle-name
renaming, and its resolved sum must agree with a direct or higher-precision
oracle.  Without those contracts the model is rejected at the corresponding
boundary rather than assigned an inferred implementation.

\begingroup
\footnotesize
\begin{longtable}{@{}L{1.75in}L{4.65in}@{}}
\toprule
\textbf{unsupported or restricted class} & \textbf{required contract} \\
\midrule
\endfirsthead
\toprule
\textbf{unsupported or restricted class} & \textbf{required contract} \\
\midrule
\endhead
additional scalar UFO functions & define a serializable
  Symbolica lowering and derivatives/branch semantics where relevant \\
adjoint $d^{abc}$ trilinears & add a physical colour basis,
  projection, contraction, and LC/NLC/full interpretation \\
epsilon and sextet tensors & add sextet current identities,
  conjugation, flow basis, and sparse colour metric before tensor lowering \\
other coloured four-point contacts & prove a complete set of
  auxiliary irreducible channels and exact reconstruction, including repeated
  representations and multiplicities \\
coloured valence above four & general representation-channel tree with
  associativity/basis-change proofs and controlled intermediate growth \\
Majorana/FNV fermions & fermion-flow orientation, charge conjugation,
  signs, wavefunctions, propagators, and closure contracts \\
spin $3/2$ & ordered Rarita--Schwinger wavefunctions, projectors,
  contractions, and tensor-component qualification \\
multiple colour groups & group-qualified representations, independent
  invariant tensors, product flow bases, and contracted colour metrics \\
general massive spin two & broader model and gauge/constraint
  validation around the existing 16-component propagator contract \\
\bottomrule
\end{longtable}
\endgroup

Validation includes successful examples and deliberately deformed tensors,
couplings, propagators, index orderings, and proof records.  This negative
coverage is part of the advertised support boundary: an unfamiliar model either
satisfies the same explicit algebraic contract or receives a diagnostic where a
new proof is required.
