% SPDX-License-Identifier: 0BSD
\section{Prepared-Model Eager DAG Execution}
\label{sec:eager-execution}

\PAC{} provides two execution contracts.  The default \emph{compiled} mode
turns a complete process stage into one or more process-specific evaluator
applications.  The opt-in \emph{eager} mode compiles the model-local vertex,
current-finalization, closure, and parameter kernels once, then represents a
process by compact invocation tables.  Rusticol interprets those tables in its
numeric core.  The modes use the same physical DAG, normalization, colour
reduction, selectors, and public APIs, but deliberately place the compilation
boundary at different levels:

\begin{center}
\small
\begin{tabular}{L{0.17\textwidth}L{0.36\textwidth}L{0.36\textwidth}}
\toprule
 & \textbf{Compiled mode} & \textbf{Eager mode} \\
\midrule
Compiled unit
  & A process-stage expression containing many current recurrences
  & One canonical model-local kernel evaluation class \\
Process generation
  & Builds and compiles process-specific stage applications
  & Rust lowers proven DAG columns to invocation, finalization, closure, reduction,
    and selector tables \\
Runtime scheduling
  & Calls a small number of wide process-stage applications
  & Gathers packets, calls reusable kernels, scatters contributions, and finalizes currents \\
Coverage contract
  & Complete artifacts support runtime selectors; selected-coverage artifacts may specialize
  & The same complete-coverage and selected-coverage contracts \\
Default
  & Yes
  & No; selected with \texttt{execution\_mode = "eager"} \\
\bottomrule
\end{tabular}
\end{center}

Eager execution is not a replacement for compiled execution.  It is a second
lane for applications where rapid process generation, reusable model kernels,
or runtime selector flexibility matters more than maximal process-wide kernel
fusion.  No eager branch is present in the compiled lane's inner loop, and the
compiled artifact contract remains unchanged.

\subsection{Prepared model and process plan}

A prepared model bundle separates model work from process work.  Schematically,
the bundle is
\begin{equation}
  \mathcal{B}_{M,b,o,t}
  = \left(
      \mathcal{I}_{M},\;
      \mathcal{E}_{M},\;
      \{K_\kappa^{(b,o,t)}\}_{\kappa\in\mathcal{K}_M},\;
      \mathcal{P}_{M}
    \right),
  \label{eq:eager-prepared-model}
\end{equation}
where \(\mathcal{I}_{M}\) is the portable compiled-model IR,
\(\mathcal{E}_{M}\) retains exact expressions, \(K_\kappa\) is one prepared
kernel for canonical evaluation class \(\kappa\), and \(\mathcal{P}_{M}\)
contains ABI and provenance metadata.  The labels \(b,o,t\) identify backend,
optimization settings, and target contract.  A bundle contains exactly one
prepared JIT, C++, or ASM backend pack.

Eager process generation keeps symbolic and numerical responsibilities
separate.  Python performs the Symbolica algebra, physics proofs,
prepared-kernel resolution, and extraction of the proven \texttt{GenericDAG}.
It then fills fixed-width columnar arrays for currents, interactions, roots,
kernel references, permutations, aliases, selector proofs, and reductions.
Rust validates those columns and lowers them directly to
\begin{equation}
  \mathcal{Q}_{P}
  = \left(
      \{\mathsf{Inv}_s,\mathsf{Att}_s,\mathsf{Fin}_s\}_{s=1}^{S},\;
      \mathsf{Close},\;\mathsf{Reduce},\;\mathsf{Select}
    \right).
  \label{eq:eager-process-plan}
\end{equation}
Here \(\mathsf{Inv}_s\) identifies kernel calls in recursion stage \(s\),
\(\mathsf{Att}_s\) maps their outputs to current components,
\(\mathsf{Fin}_s\) applies the current's finalization or propagator once,
\(\mathsf{Close}\) builds amplitudes, and \(\mathsf{Reduce}\) performs the
physical colour/helicity contraction.  \(\mathsf{Select}\) stores dependency
domains for runtime selectors.  The Rust lowering assigns slots, interns
selector domains, groups invocations, schedules attachments and finalizations,
constructs closures and coherent reductions, validates the resulting plan, and
writes the indexed binary runtime layout.  It does not return expanded Python
row objects or construct a large JSON runtime schema.

No backend evaluator is built or compiled during this process step.  Invocation
rows refer to kernels already present in \(\mathcal{B}\), and the referenced
prepared applications are copied into the standalone process artifact.  The
cost of preparing \(\mathcal{B}\) is therefore a separate model-level quantity,
not part of eager process-generation time.

Prepared kernels are derived from the same verified oriented-kernel catalog
used by the model-generic UFO lowering.  The built-in Standard Model emits that
same catalog, while its explicitly Standard-Model-specific physics remains
under \path{src/pyamplicol/models/builtin/}.  Couplings, colour coefficients,
exchange signs, input permutations, and proof factors are invocation metadata,
not distinct compiled applications.  Existing proof-gated auxiliary-current
decompositions continue to reduce supported higher-point interactions to the
same local kernel classes described here and in the UFO-support section below.

\subsection{Stage execution}

Let \(V_{c\alpha p}\) be component \(\alpha\) of current slot \(c\) at phase-space
point \(p\).  An invocation row \(r\) stores a kernel identifier \(\kappa(r)\),
input slots and component permutations, momentum slots, coupling references,
an exact factor \(w_r\), and an output attachment.  For one stage, Rusticol
first forms unpropagated current components
\begin{equation}
  U_{c\alpha p}^{(s)} =
  \sum_{r\in\mathcal{R}_s(c,\alpha)}
    w_r\,
    \left[
      K_{\kappa(r)}
      \left(
        G_r(V_{\cdot\cdot p}),\;q_r(p),\;\theta
      \right)
    \right]_{\alpha(r)} .
  \label{eq:eager-invocation-sum}
\end{equation}
The gather map \(G_r\) is fixed by the invocation table.  Contributions are
accumulated before current finalization, so a current with momentum \(Q_c\) is
materialized exactly once:
\begin{equation}
  V_{c\beta p}^{(s)} =
  \left[F_{\phi(c)}\left(U_{c\cdot p}^{(s)},Q_c(p),\theta\right)\right]_\beta .
  \label{eq:eager-finalization}
\end{equation}
The finalization class \(\phi(c)\) may be an identity, a propagator, or another
model-proved current transformation.  This ordering prevents a propagator from
being applied once per contributing vertex and preserves the compiled-mode
normalization convention.

After the last recursion stage, closure rows produce amplitude components,
\begin{equation}
  A_{h\gamma p}
  = \sum_{r\in\mathcal{C}(h,\gamma)}
      w_r^{\mathrm{cl}}
      K_{\kappa(r)}^{\mathrm{cl}}
      \left(G_r^{\mathrm{cl}}(V_{\cdot\cdot p}),q_r(p),\theta\right),
  \label{eq:eager-closure}
\end{equation}
and the existing LC or contracted-colour reduction computes the requested
total or resolved observable.  In a contracted basis this has the schematic
form
\begin{equation}
  \mathcal{M}_p =
  \mathcal{N}\sum_h\sum_{\gamma,\delta}
  A_{h\gamma p}\,C_{\gamma\delta}\,A^*_{h\delta p},
  \label{eq:eager-reduction}
\end{equation}
with the same colour matrix \(C\), symmetry factors, initial-state average,
and coupling normalization as compiled mode.

The Rust implementation is deliberately separate from compiled execution.
Plan loading and validation are in
\path{rust/crates/rusticol-core/src/eager_runtime/plan.rs}; the allocation-free
numeric loop is in \path{eager_runtime/execute.rs}; runtime ownership and
workspace reuse are in \path{eager_runtime/runtime.rs}.  The artifact-facing
integration is isolated under \path{rusticol-core/src/engine/eager_*.rs}.

\subsection{Packetization, tiling, and allocation discipline}

Rusticol does not call a backend once per DAG edge.  Invocation rows are
packetized by kernel class and compatible mapping.  For a tile of \(T\) points,
the innermost layout keeps points contiguous,
\begin{equation}
  X[\text{argument}][\text{invocation}][\text{point}],
  \label{eq:eager-packet-layout}
\end{equation}
so a SymJIT application can auto-vectorize across points.  C++ and ASM packs
receive the same batched packet but remain scalar across rows; no SIMD claim is
made for those backends.

Current storage is component-major with points contiguous.  Gather buffers,
kernel outputs, current storage, selector masks, closure storage, and reduction
workspace are allocated at load or selector change and then reused.  After
warm-up, \texttt{evaluate\_into} performs no heap allocation in the Rust numeric
core.  Large batches are tiled using
\begin{equation}
  T_{\mathrm{eff}} = \min\!\left(
    T_{\mathrm{requested}},
    \left\lfloor\frac{W_{\mathrm{limit}}}{W_{\mathrm{per\ point}}}\right\rfloor
  \right),
  \label{eq:eager-workspace-tile}
\end{equation}
subject to a minimum valid packet.  The public defaults are a requested tile
size of 1024 points and a 256 MiB workspace.  This keeps memory bounded for
arbitrarily large Monte-Carlo batches without placing Python or NumPy packing
inside the reported Rusticol wall time.

Eager profiling separates initialization, gather, kernel calls, invocation
scatter, finalization, finalization scatter, closure, reduction, and copy-out.
Those markers are returned by \texttt{pyamplicol profile} and the same native
runtime profile used by Python, C11, C++17, Fortran 2008, and Rust 2021 clients.
The report's eager \texttt{eval} field is the inclusive eager execution lane,
not kernel-call time alone; the detailed profile separates its constituent
phases.

\subsection{Runtime selectors and complete LC coverage}

For a selector \(\sigma\), eager lowering stores a dependency domain
\(D(x)\) for each invocation, attachment, finalization, and closure row \(x\).
The active schedule is
\begin{equation}
  \mathcal{Q}_{P}(\sigma)
  = \{x\in\mathcal{Q}_{P}:D(x)\cap\sigma\neq\varnothing\},
  \label{eq:eager-selector-closure}
\end{equation}
including all transitive current dependencies.  Masks and packet schedules are
rebuilt only when a selector changes, not at every phase-space point.

This distinction is important for LC timing.  Every \emph{complete} eager LC
artifact contains each physical flow and generated helicity component.  A
caller may select any one flow for a helicity sum, one helicity for all flows,
or any supported subset at runtime.  The flow identifier, for example
\texttt{flow:3,1,2,5,6,7,4}, is therefore a runtime choice rather than a flow
hard-wired during process generation.  A deliberately selected-coverage eager
artifact remains limited to the components that were generated.

Compiled mode exposes the same complete-coverage runtime contract.  Coverage
does not, however, prescribe one execution graph.  As described in
Sec.~\ref{sec:lc-flow-layouts}, both execution modes provide topology-replay
and all-flow-union layouts.  The report uses topology replay for
single-flow/helicity-sum and the all-flow union for
all-flows/single-helicity, with separate process-generation times.  Either
artifact can choose any retained flow or helicity without regeneration.
Deliberately specialized artifacts remain useful as optimization baselines,
but are not the reusable report workloads.

\subsection{Artifact, precision, and portability contracts}

An eager process artifact is standalone.  It copies each referenced prepared
kernel exactly once under the artifact root and never depends on the original
prepared-model path.  Fixed-width little-endian tables use 32-bit identifiers
and 64-bit offsets/counts.  Plan-v3 artifacts use runtime kind
\texttt{pyamplicol-runtime-eager-execution}, capability
\texttt{rusticol.eager-runtime-layout.complex-f64.v1}, and four complementary
records:
\begin{itemize}
  \item a small \path{execution.json} summary containing identity, ABI,
        provenance, counts, digests, options, and inspection statistics;
  \item a compact \path{physics.json} containing public process axes, coverage,
        selector metadata, parameters, normalization, and proof summaries;
  \item \path{processes/<id>/eager-runtime.pacbin}, containing the
        process-local invocation, slot, selector, closure, reduction, and proof
        tables; and
  \item the artifact-root \path{evaluators.pacbin}, containing indexed prepared
        evaluators and their exact states.
\end{itemize}

High-cardinality runtime data is not duplicated in JSON.  Rusticol
authenticates the artifact and PACBIN indices, memory-maps the containers, and
decodes the eager layout into a validated owned execution plan.  Normal
\texttt{inspect} operations use the summary metadata rather than scanning every
table.  The loader rejects malformed offsets, unknown kernel identifiers,
incompatible ABIs, and target mismatches before entering native evaluation.

This representation reduces Python object construction, JSON serialization,
filesystem entry count, artifact footprint, peak generation memory, and cold
load work.  It does not change the eager numerical schedule: topology replay,
LC all-flow union, NLC/full contraction, aliases, structural zeros, and global
or per-point selectors retain their existing semantics.  Both LC layouts use
the same Rust lowering and compact container contract.  Exact Python execution
reads the same indexed plan and evaluator states.  Target-native C++ and ASM
libraries remain separate payloads.

Plan-v3 is the eager artifact compatibility boundary.  Earlier eager artifacts
use an expanded runtime representation and must be regenerated; the loader
identifies that capability before opening the old high-cardinality payload and
reports the required regeneration.  This requirement is limited to eager
artifacts and does not change compiled artifacts or prepared-model bundles.

JIT packs store SymJIT application state rather than final machine code.  The
portable SymJIT storage v3 contract is available at optimization level 2, and
the receiving host rebuilds executable code for its CPU.  Wheels therefore
carry the built-in-SM \texttt{built-in-sm-jit-o2} prepared pack.  pyAmpliCol
forces O2 when preparing JIT kernels, including when another level was
requested.  This does not change process-local compiled DAG evaluators, whose
independent configuration may use O3.  Prepared C++ and ASM packs remain
target-native.

Symbolica is required during eager generation and for non-f64 exact execution.
After generation, saved JIT applications support Symbolica-free f64 execution,
including multicore use.  Exact expressions remain in the artifact, and
\path{src/pyamplicol/runtime/eager_exact/} executes the same plan for
double-double and arbitrary precision.  Thus the execution-mode choice does
not change the public precision contract.

\subsection{Performance interpretation and scaling}

Eager process-generation timing begins with an already prepared model bundle
and ends with an authenticated, loadable process artifact.  It includes Python
proof/DAG extraction, transfer-column construction, Rust plan lowering, compact
container writing, and post-build validation.  Prepared-model creation is
reported separately.  Useful comparisons therefore report process generation,
prepared-model creation, artifact size, peak resident memory, authenticated
cold load, and first-use break-even as distinct quantities.

Rust table lowering and high-cardinality serialization handle the part of
eager generation that grows with the process DAG.  Compact PACBIN storage also
avoids materializing equivalent expanded Python and JSON objects.
The resulting benefit depends on current count, selector-domain complexity,
colour contraction, and proof metadata; it is not represented by one universal
speedup.  Published process and $Z$-ladder tables provide the measured values
under the benchmark contract defined in the main methodology section.

For runtime, eager mode avoids process-specific backend compilation but pays
explicit gather, scatter, finalization, and reusable-kernel dispatch.  SymJIT
amortizes those costs over point batches through internal SIMD.  Selector
measurements distinguish homogeneous, already grouped, alternating, and random
per-point selections because regrouping and SIMD occupancy can change the wall
time without changing the matrix element.  A separately specialized compiled
stage can remain faster for some selectors; fusing entire recurrence regions
would instead reproduce the compiled mode's process-specific applications.

\subsection{Choosing the mode}

Use compiled mode when process generation is affordable and the target
workload benefits from process-wide specialization.  Use eager mode when many
processes share one model, when generation time dominates, or when one artifact
must support changing LC flow/helicity selections.  The common built-in-SM JIT
O2 prepared-kernel path needs only

\begin{lstlisting}[language=bash]
pyamplicol generate "d d~ > z g g g" artifacts/ddbar_z3g_eager \
  --model built-in-sm --execution-mode eager --color-accuracy nlc
\end{lstlisting}

External models and C++/ASM backends first require an explicit
\texttt{pyamplicol model compile} prepared bundle.  Missing or mismatched packs
fail before DAG construction with the exact preparation command; eager
generation never silently compiles a backend pack.
