% SPDX-License-Identifier: 0BSD
\section{Reusable Leading-Colour Execution Layouts}
\label{sec:lc-flow-layouts}

Leading-colour coverage and leading-colour execution layout are separate
contracts.  Let \(\mathcal H\) be the retained physical helicity IDs and let
\(\mathcal F\) be the retained physical colour-flow IDs.  A complete LC
artifact represents
\begin{equation}
  \mathcal C_{\mathrm{LC}}=\mathcal H\times\mathcal F
  \label{eq:lc-complete-coverage}
\end{equation}
and can therefore expose every resolved component
\(\mathcal A_{h f}\), independently of how its recurrence is scheduled.  For
runtime-selected subsets \(S_H\subseteq\mathcal H\) and
\(S_F\subseteq\mathcal F\), Rusticol computes
\begin{equation}
  \mathcal W(S_H,S_F)
  =\mathcal N\sum_{h\in S_H}\sum_{f\in S_F}w_{hf}
   \left|\sum_{r\in G(h,f)}\mathcal A^{(r)}_{hf}\right|^2 .
  \label{eq:lc-runtime-selection}
\end{equation}
Here \(G(h,f)\) is one coherent root group, \(w_{hf}\) contains the exact
symmetry and LC weights, and \(\mathcal N\) is the process normalization.  A
layout changes the representation and order used to evaluate these terms; it
does not change \(\mathcal H\), \(\mathcal F\), or Eq.~\eqref{eq:lc-runtime-selection}.

\subsection{Two complete-coverage layouts}

\PAC{} provides two LC layouts because the two principal workloads expose
different opportunities for current sharing.

\begin{center}
\small
\begin{tabular}{@{}L{1.26in}L{2.42in}L{2.42in}@{}}
\toprule
\textbf{property} & \textbf{\texttt{topology-replay}} &
  \textbf{\texttt{all-flow-union}} \\
\midrule
Primary workload & one runtime-selected flow, summed helicities &
  all flows, one runtime-selected helicity \\
Retained physics & every physical flow and helicity &
  every physical flow and helicity \\
Main reuse & exact flow-topology representatives, label permutations,
  signs, and multiplicities & currents, interactions, and closures shared
  directly across the union of physical flows \\
Compiled lane & representative fused stage recurrences replayed by Rusticol &
  fused cross-flow union stages selected by runtime helicity \\
Eager lane & prepared-kernel invocations scheduled by replay class &
  prepared-kernel invocations lowered from the same cross-flow union \\
Default & yes & explicit opt-in \\
\bottomrule
\end{tabular}
\end{center}

In the topology-replay layout, exact certificates partition physical flows
into recurrence classes.  If \(\rho(f)\) is the representative of the class
containing \(f\), the artifact records a source-label permutation \(\pi_f\),
an exact sign or factor \(s_f\), and its reduction weight.  Schematically,
\begin{equation}
  \mathcal A_{h f}(p)
  =s_f\,\mathcal A_{\pi_f(h),\rho(f)}\!\left(\pi_f(p)\right).
  \label{eq:lc-topology-replay}
\end{equation}
Rusticol maps the requested flow to its representative, groups compatible
point rows, evaluates contiguous backend batches, and scatters the weighted
result to the public flow ID.  This avoids materializing one independent DAG
for every physical ordering and is the layout used for the
single-flow/helicity-sum benchmark.

The all-flow-union layout instead constructs the complete cross-flow current
DAG before evaluator lowering.  If \(D_{hf}\) is the dependency graph of one
resolved component, its graph is the exact quotient
\begin{equation}
  D_{\mathrm{union}}
  =\left(\bigcup_{h\in\mathcal H,\,f\in\mathcal F}D_{hf}\right)
   \big/\!\sim ,
  \label{eq:lc-all-flow-union}
\end{equation}
where \(\sim\) identifies currents, kernel evaluations, attachments, and
closures whose canonical contracts prove them equal up to stored factors.
For a selected helicity, one sweep of this union shares common intermediate
currents across all requested flows.  This is the layout used for the
all-flows/single-helicity benchmark.  The artifact does not also carry a
second topology-replay graph or a generation-fixed-helicity graph.

Both layouts are available with compiled and eager execution.  Compiled mode
lowers the chosen graph to process-specific stage evaluators.  Eager mode
lowers it to invocation tables over the prepared model kernels.  Thus
\texttt{execution\_mode} selects how numerical kernels are supplied, while
\texttt{lc\_flow\_layout} selects how complete LC recurrence work is shared.

\subsection{Runtime selectors}

Public selectors always use the stable IDs stored in the physics manifest,
such as \path{flow:2,5,4,1} and \path{h:-1,+1,+0,-1,+1}.  Batch-global
\texttt{color\_flows} and \texttt{helicities} select rectangular subsets of
Eq.~\eqref{eq:lc-complete-coverage}.  The per-point
\texttt{color\_flow\_}\allowbreak\texttt{by\_point} and
\texttt{helicity\_}\allowbreak\texttt{by\_point} inputs select one component
on the corresponding axis for each point.  A global and a per-point selector
are mutually exclusive on the same axis.  Omitting an axis sums every retained
component on that axis.

Rusticol stably groups per-point selector rows before numerical evaluation so
that equal selectors form contiguous SIMD-compatible packets.  An already
grouped input remains in order and does not pay for a redundant sort.  This
selector planning is a runtime operation; it does not reduce the generated
coverage of either layout.  Deliberately generation-sliced artifacts remain a
separate expert facility and, by construction, can select only components
that were retained during their generation.  The all-flow-union layout
requires complete flow and helicity coverage and therefore rejects such
generation slices.

The layout is selected in a run card with
\begin{lstlisting}
[color]
accuracy = "lc"
lc_flow_layout = "all-flow-union"
\end{lstlisting}
or with \texttt{--lc-flow-layout all-flow-union}.  Omitting the option keeps
the \texttt{topology-replay} default.

\subsection{Why the report has two generation times}

The two layouts retain the same physical component set but build different
graphs, evaluator payloads, and runtime schedules.  Their process-generation
times are consequently distinct observables,
\begin{equation}
  T_{\mathrm{gen}}^{\mathrm{replay}}
  \quad\hbox{and}\quad
  T_{\mathrm{gen}}^{\mathrm{union}},
  \label{eq:lc-two-generation-times}
\end{equation}
and neither value is copied into the other workload's table slot.  The LC
selected-flow/helicity-sum columns use
\(T_{\mathrm{gen}}^{\mathrm{replay}}\); the all-flows/single-helicity columns
use \(T_{\mathrm{gen}}^{\mathrm{union}}\).  Original \AC{} produces one
table-driven library for both workloads, so its one generation time remains
the denominator of both \PAC{}/\AC{} ratios.  In eager-versus-compiled tables,
each eager generation is compared with the compiled generation using the
same LC layout.  Prepared-model creation is a reusable model-level operation
and remains outside either eager process-generation timer.

\subsection{NLC and full colour}

The layout option applies only to LC.  NLC and full-colour artifacts already
construct one complete amplitude basis and contract it with a sparse colour
metric,
\begin{equation}
  \mathcal W_{\mathrm{contracted}}
  =\mathcal N\sum_h\sum_{a,b}
   \mathcal A_{ha}^{*}\,C_{ab}\,\mathcal A_{hb}.
  \label{eq:contracted-colour-layout}
\end{equation}
They do not expose the physical LC-flow axis whose alternative scheduling
motivates topology replay and the all-flow union.  Configuration therefore
rejects \texttt{all-flow-union} for NLC and full colour.  Their generation,
contraction, cache, and runtime contracts are unchanged by this choice.
